Sensitivity Analysis

### 2022-12-08 analysis/alt_analysis.Rmd

---
title: "Analysis"
author: "Martin Hinz"
date: '2022-04-04'
output:
  html_document:
    keep_md: true
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(OPENSSL_CONF="/etc/ssl/")
if (!webshot::is_phantomjs_installed()) webshot::install_phantomjs()
library(magick)
```

@@

Running through the analysis can take a long time, especially the Bayesian model. We point out the long runtimes again at the appropriate place. Also, you might need at least 64 GB of RAM to avoid crashes due to missing memory.

@@

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(mapview)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
library(grid)
```

@@

For the aorist analysis we also use the package aoristAAR, which is not available on CRAN, but would have to be installed directly from GitHub:

```{r message=FALSE}
if(!require('devtools')) install.packages('devtools')
library(devtools)
install_github('ISAAKiel/aoristAAR')
require(aoristAAR)
```
Also, neotoma is not longer available on cran, and it has been replaced by neotoma2, so we had to replace it. That is why we have to load it again:

```{r}
if(!require('neotoma2')) devtools::install_github('NeotomaDB/neotoma2')
require(neotoma2)
```

## Data collection

The data used in this analysis are the following proxies obtained from the following sources:

-   An openness index generated by a PCA of five pollen profiles in the Swiss Plateau from the neotoma database [@williams2018].

-   ^14^C sum calibration, data sets from the XRONOS database as well as from the unpublished PhD thesis of Julian Laabs [@laabs2019] and from the data collection of [@martínez-grau2021].

-   Sites from the database of the Cantonal Archaeology <!--# which! --> as the basis of an aoristic analysis

-   The number of dated fell phases at lakeshore settlements in the Three Lakes Region from the doctoral thesis by Julian Laabs [\@laabs2019].

### Openness index

We start with the openness index, as this will set the spatial framework for our analyses. The five pollen profiles are the following:

```{r}
pollen_locations <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "pollen_locations.csv")))
pollen_locations
```

We can also map these. To do this, we first transform the coordinate system into the Swiss national coordinate system, and then display them:

```{r}
pollen_locations.sf <- st_as_sf(pollen_locations,
                                coords = c("lng", "lat"), # coordinate columns
                                crs = 4326)  # coordinate references system in epsg))
pollen_locations.sf.lv95 <- st_transform(pollen_locations.sf, crs = 2056)

pollenmap <- tempfile(fileext = ".png")
mapshot(
  mapview(pollen_locations.sf),
  file = pollenmap
  )

img <- magick::image_read(pollenmap)
old.par <- par(mar = c(0, 0, 0, 0))
plot(img)
par(old.par)
```

We download the data from neotoma:

```{r message=FALSE, warning=FALSE}
pollen_data <- get_downloads(pollen_locations$neotoma_id, all_data=T)
```

Then we load a few help scripts which can be found under "code/neotoma_helpers.R".

```{r}
source(file = normalizePath(file.path(here(), "code", "neotoma_helpers.R")))
```

Now we filter the data sets so that we only retain the pollen data that record "NISP".

```{r}
pollen_data.samples <- samples(pollen_data)

pollen_data.samples.filtered <- pollen_data.samples %>% subset(element == "pollen" & units == "NISP")
```

Then we convert the NISP into percentages:

```{r}
pollen_data_comp <- transform_to_percent(pollen_data.samples.filtered)
```

Furthermore, we need a (handwritten) concordance list for the taxa names:

```{r}
common_names <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "species.csv")), row.names = 1)
common_names
```

With this concordance table we combine the species with respect to their genus:

```{r}
pollen_data_comp <- aggregate_by_joint_name(pollen_data_comp, common_names = common_names)
```

Now we can combine the individual pollen profiles into an overall table, where each row represents a sample:

```{r}
all_output <- pollen_data_comp
```

We restrict the data set to the Holocene so that we no longer have the pre-Holocene developments in the principal component analysis:

```{r}
timeframe <- c(-7000,-1000)
all_output <- subset(all_output, 1950-age > timeframe[1] & 1950-age < timeframe[2])
all_output[is.na(all_output)] <- 0
```

Then we extract the actual data:

```{r}
all_data <- all_output[, !(colnames(all_output) %in%  c("age", "sampleid", "sitename"))]
```

We then filter the data. Only those taxa are considered which are present in at least 1/3 of all data series:

```{r}
all_data <- all_data[ , colSums(all_data) != 0]
all_data <- all_data[,colSums(all_data>0)>(nrow(all_data)/3)]
```

In addition, only those with an average frequency greater than 0.1% are included:

```{r}
all_data <- all_data[,colMeans(all_data)>0.1]
```

However, we add the *cerealia* back in, regardless of their frequency:

```{r}
if(!("Cerealia" %in% colnames(all_data)))
{
  all_data <- data.frame(all_data, Cerealia = all_output[,"Cerealia"])  
}
```

These data can now be evaluated by means of a principal component analysis:

```{r}
res.pca <- rda(all_data, scale = TRUE)
biplot(res.pca, type="text")
```

This calculation already shows the familiar structure that we have the known open land indicators at one end of the spectrum and the forest species (tree pollen) at the other. However, the result is also influenced by a gradient which has nothing to do with the effect we are interested in: The immigration of beech. To eliminate this gradient, we use a partial RDA in which only the residuals for Fagus are evaluated:

```{r}
res.pca <- rda(all_data ~ Condition(Fagus), data=all_data, scale = TRUE)
biplot(res.pca, type="text")
```

From this principal component analysis, we now extract the first dimension as the openness index, and supplement it with the datings of the individual samples. In doing so, we ensure that open land indicators end up on the positive side of the result vector:

```{r}
orientation <- sign(scores(res.pca)$species["Cerealia",1])
res.open <- data.frame(scores(res.pca, choices = 1, display = "si")*orientation)
colnames(res.open) <- "score"
res.open$age <- all_output$age
res.open$site <- all_output$sitename
ggplot(res.open) + geom_line(aes(x = 1950-age, y = score, color = site))
```

The individual profiles show a very similar development over time. We now summarise the common trend and smooth it with a 50-year moving window. For this, however, we first have to interpolate shared points in time, which we do via a linear approximation:

sw <- 50

full_range <- full_seq(res.open$age, 1)

res.open.interpolated <- by(res.open, res.open$site, function(x) approx(x$age,x$score, full_range)$y)

res.open.interpolated <- data.frame(do.call(cbind, res.open.interpolated))

res.open.interpolated$age <- full_range

res.open.interpolated <- melt(res.open.interpolated, id.vars=c("age"))

res.open.interpolated$site <- res.open.interpolated$variable

res.open.interpolated$variable <- NULL

res.open_smoothed <- res.open.interpolated %>% 
  group_by(site) %>%
  # RcppRoll::roll_mean() is written in C++ for speed 
  mutate(moving_mean = roll_mean(value, sw, fill = NA, na.rm = TRUE))

res.open_smoothed$value<-NULL
res.open_smoothed <- na.omit(res.open_smoothed)
```

Then we pick every 50th date:

```{r pollenproxy}
res.open_smoothed <- res.open_smoothed[res.open_smoothed$age %in%
seq(from=1000,
    to=10000, by=50),]
pollenproxy_plot <- ggplot(res.open_smoothed,aes(x=1950-age,y=moving_mean)) +
  geom_point(aes(color=site), alpha =.5) +
  geom_smooth(span = 0.05, color = "black") +
  scale_x_continuous(breaks=seq(timeframe[1],timeframe[2],200), limits = timeframe) +
  labs(y = "Openness score [PCA]",x = "Date",colour = "Sites") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
pollenproxy_plot
```
We save this plot for later use:

```{r}
ggsave(normalizePath(file.path(here(), "figures","pollenproxy.pdf"), mustWork = F),
       plot = pollenproxy_plot, width = 21, height = 29.7/2, units = "cm")
```

Finally, we calculate the average of all profiles as the final supra-regional openness index.

```{r}
res.open_final <- res.open_smoothed %>%
  group_by(age) %>%
  mutate(mean=mean(moving_mean),
         sd = sd(moving_mean)) %>% 
  select(age,mean,sd) %>%
  unique()  %>% arrange(desc(age))

ggplot(res.open_final,aes(x=1950-age)) +
  geom_line(aes(y=mean)) +
  geom_segment(aes(y=mean-sd, yend =mean+sd, xend=1950-age), alpha = .25)
```

### ^14^C Summenkalibration

The data set for the 14C sum calibration is composed of the above-mentioned sources.

```{r}
c14 <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "14c_swiss_plateau.csv")))
```

We can show this on the map:

```{r}
c14map <- tempfile(fileext = ".png")
mapshot(
  mapview(st_as_sf(c14,
                   coords = c("lng", "lat"), 
                   crs = 4326),layer.name = "14C Data"
          ),
  file = c14map
  )

img <- magick::image_read(c14map)
old.par <- par(mar = c(0, 0, 0, 0))
plot(img)
par(old.par)
```

Next, we calibrate the 14C data using rcarbon: <!--# uncal vs cal? -->

```{r}
c14.calibrated <- calibrate(x = c14$bp, errors = c14$std, verbose = F)
```

Subsequently, we perform the sum calibration, whereby we perform a binning at the level of the sites:

```{r}
sumcal <- spd(c14.calibrated, timeRange = 1950-timeframe, bins = c14$site, runm = sw, verbose = F)
```

Below is the visualisation of the sum calibration:

```{r}
plot(1950-sumcal$grid$calBP, sumcal$grid$PrDens,type="l", main = paste0("n=", length(c14.calibrated)))

```

Finally, we extract the values every 50 years:

```{r}
res.sumcal <- sumcal$grid[sumcal$grid$calBP %in%
seq(from=1000,
    to=10000, by=50),]
```

### Aoristic Site Count

The third proxy is the aoristic sum of the number of sites from the cantonal archaeology database. For these, we have obscured the coordinates to avoid the well-known problems that can arise from clear site coordinates.

```{r}
sites <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "site_data_fuzzy.csv")))
```

We can depict this on the map:

```{r}
sitesmap <- tempfile(fileext = ".png")
mapshot(
  mapview(st_as_sf(sites,
                   coords = c("LV03_Rechtswert_fuzzy", "LV03_Hochwert_fuzzy"),
                   crs = 21781),
          layer.name = "Sites"
  ),
  file = sitesmap
)
img <- magick::image_read(sitesmap)
old.par <- par(mar = c(0, 0, 0, 0))
plot(img)
par(old.par)
```

The dates come in two categories, rough and very rough We use the rough datings where they are available. Where they are not, we fall back on the very rough dates. But first we load the concordance table:

chrono_rough <- read.csv(file = normalizePath(
  file.path(here(), "data","raw_data", "chrono_rough.csv")
  ),
  row.names = 1)

chrono_vrough <- read.csv(file = normalizePath(
  file.path(here(), "data","raw_data", "chrono_very_rough.csv")
  ),
  row.names = 1)
```

Next, we prepare the beginning and end as a column:

```{r}
sites$begin <- NA
sites$end <- NA
```

And then we first fill these columns with the data from the very rough dating:

```{r}
for(i in 1:nrow(chrono_vrough)){
  this_phase <- chrono_vrough[i,]
  sites$begin[sites$chrono_very_rough == this_phase[,1]] <- this_phase$dat_begin
  sites$end[sites$chrono_very_rough == this_phase[,1]] <- this_phase$dat_end
}
```

Where available, we overwrite the very rough dating with the rough dating:

```{r}
for(i in 1:nrow(chrono_rough)){
  this_phase <- chrono_rough[i,]
  sites$begin[sites$chrono_rough == this_phase[,1]] <- this_phase$dat_begin
  sites$end[sites$chrono_rough == this_phase[,1]] <- this_phase$dat_end
}
```

However, this does not allow for a very precise dating:

```{r}
table(sites$begin)
```

Nevertheless, we next use the aorist sum as a mapping of the expected value for simultaneously existing settlements:

```{r}
res.aorist <- aorist(sites, from = "begin", to = "end", method = "weight")

res.aorist$age <- 1950-res.aorist$date
res.aorist <- subset(res.aorist, date >= timeframe[1] & date <= timeframe[2])
```

Again, the curve of the proxy is plotted here also:

```{r}
plot(res.aorist$date, res.aorist$sum,type="l", main = paste0("n=", nrow(sites)))
```

Once more, we extract the values every 50 years:

```{r}
res.aorist <- res.aorist[res.aorist$age %in%
seq(from=1000,
    to=10000, by=50),]
```

### Dendro Dated Settlements

This year-by-year dataset maps the number of lakeshore settlements in the Three Lakes Region. Details can be found in the publication by [@laabs2019]. To match the resolution of the other datasets, this dataset is also sampled at 50-year intervals, and smoothed accordingly beforehand using a moving average.

First we load the data:

```{r}
lss <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "dendro_years.csv")))
```

Then we complete the data set so that it covers the entire period under consideration:

```{r}
lss <- rbind(data.frame(date=-7050:min(lss$date)-1,n_settlements=0),
             lss,
             data.frame(date=max(lss$date)+1:-1,n_settlements=0))
```

Finally, we run a moving average over it with the same window as for the other data sets:

```{r}
res.lss <- lss %>% 
  mutate(moving_mean = roll_mean(n_settlements, sw, fill = NA, na.rm = TRUE))
```

Here is yet another plot of the resulting curve:

```{r}
plot(res.lss$date, res.lss$moving_mean,type="l")
```

Picking the data points every 50 years again:

```{r}
res.lss <- res.lss[res.lss$date %in% seq(from=timeframe[1],
                                         to=timeframe[2], by=50),
        ]
res.lss$age <- 1950-res.lss$date
```

### Combining the proxies

Thus we have all proxies available, and can display them (scaled) all together:

```{r}
ggplot() +
  geom_line(data = res.open_final, aes(x = 1950-age, y = scale(mean)), col="darkgreen", alpha = 0.75) +
  geom_line(data = res.sumcal, aes(x = 1950-calBP, y = scale(PrDens)), col="red", alpha = 0.75) +
  geom_line(data = res.aorist, aes(x = date, y = scale(sum)), col="gray", alpha = 0.75) + 
  geom_line(data = res.lss, aes(x = date, y = scale(moving_mean)), col="brown", alpha = 0.75) +
  scale_colour_manual(values = c("darkgreen", "red", "gray", "brown"),
                      labels = c("Openness Indicator", "Sum Calibration", "Aoristic Sum", "Dendro Dated Settlements")
                      )
```

We merge the dataset and restrict it to our observation window:

```{r}
all_proxies <- merge(res.sumcal, res.open_final, by.x = "calBP", by.y = "age") %>%
  merge(res.aorist, by.x = "calBP", by.y = "age") %>%
  merge(res.lss, by.x = "calBP", by.y = "age") %>%
  select(calBP, PrDens, mean, sum, moving_mean) %>%
  rename(age = calBP, sumcal = PrDens, openness = mean, aoristic_sum = sum, dendro = moving_mean) %>%
  dplyr::filter(age < 8000 & age > 3000)

all_proxies
```

We might like to store the result for the actual analysis:

```{r}
write.csv(all_proxies, file = normalizePath(
  file.path(here(), "data","preprocessed_data", "all_proxies.csv"
            ),
  mustWork = F)
  )
```

## Transforming the Data

If the data has already been created in a previous run, we can also reload it directly at this point:

@@

@@

The actual model consists of a nimble code block that describes the relationships and sets the priors for the parameters:

@@

  # Autoregressive process for remaining years
  for(t in 2:(nYears)) {
    # The actual number of sites per year
    nSites[t] ~ dpois(lambda[t])

@@

@@

```{r}
model_monitors <- c("PopDens", "p")
```

@@

# Spare 4 cores from the calculation
ncore <- detectCores() - 4
ncore <- max(ncore, 1)

@@

```{r}
# Initialize with non-convergence
converged <- F

@@

  # run the model for another batch, with resetting the values (burn-in)
  mcmcSamples <- clusterEvalQ(cl, {
    CmodelMCMC$run(batches, reset = FALSE, resetMV = TRUE)
    return(as.mcmc(as.matrix(CmodelMCMC$mvSamples)))
  })

@@

  # optional: create an mcmc traceplot for visual inspection
  #MCMCtrace(window(mcmcSamples, start = (batches/thinning)-min((batches/thinning),5000)), params = "PopDens", pdf = F)
}

@@

@@

The model trusts mainly the openness index, the aoristic sum and the dendro data play a subordinate role. The sum calibration has a higher weight. However, the shape of the distributions also indicates that we may have too few effective samples to make a reliable statement about the highest posterior density intervals. Let's take a look at the effective samples:

@@

@@

  # just in case: store the result in a RDS file for later inspection  
  saveRDS(collector, file = "mcmc_collector.RDS")
}

@@

@@

```{r}
collector <- readRDS("mcmc_collector.RDS")
```

@@

# MCMCvis methods are rather memory intensive. We implement the summary from scratch
all_chains <- as.matrix(collector)

@@

```{r}
PopDens_summary <- this_mcmc_summary[grep("^PopDens", params),]
PopDens_summary$age <- rev(all_proxies_orig$age)
write.csv(PopDens_summary,
          file = normalizePath(
            file.path(here(), "data","preprocessed_data", "popdens_summary.csv"
                      ),
            mustWork = F)
          )
```

@@

proxies_and_result <- rbind(melt(all_proxies_orig, id.vars = "age"),
                            melt(PopDens_summary[,2:5], id.vars = "age")
)

@@

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popdens_estimation.pdf"), mustWork = F),
       plot = popdens_plot_adjusted, width = 21, height = 29.7/2, units = "cm")
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","p_estimation.pdf"), mustWork = F),
       plot = p_plot, width = 21, height = 29.7/2, units = "cm")
```
Also interesting is the variation coefficient from the estimation of the Population density:

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popvar_plot.pdf"), mustWork = F),
       plot = popvar_plot, width = 21, height = 29.7/2, units = "cm")
```

>>>>

---
title: "Analysis"
author: "Martin Hinz"
date: '2022-04-04'
output:
  html_document:
    keep_md: true
bibliography: references.bib
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

In the review of the article, the model and the associated analysis, it was noted that the model we use is too constrained by the Poisson process. We are convinced that the Poisson process is the right choice to model a settlement number as a process autocorrelated over time. Nevertheless, we are happy to modify the model accordingly to show the differences. This document contains the corresponding alternative version of the model and its results.

As with the original model: Running through the analysis can take a long time, especially the Bayesian model. We point out the long runtimes again at the appropriate place. Also, you might need at least 64 GB of RAM to avoid crashes due to missing memory.

@@

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
#library(RcppRoll)
#library(sf)
#library(mapview)
#library(vegan)
#library(neotoma)
#library(analogue)
#library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
library(grid)
```

@@

## Loading and transforming the preprocessed data

First we load the pre-processed data:

@@

Then we carry out the transformation steps as we did in the actual analysis.

@@

The actual model consists of a nimble code block that describes the relationships and sets the priors for the parameters. It should be noted that we have changed the function for the number of settlements, and thus the proposal distribution. It is now a Negative Binomial Distribution, where both the expected value and the variance can vary. The expected value is still derived from $\lambda_t$, but this is integrated into the model via a success parameter $prob_t$, which results as follows:

$$
prob_t = \frac{r}{r+\lambda_t}
$$

The parameter $r$ used here and also in the distribution itself is the one that determines the overdispersion and thus makes the variance variable compared to a Poisson distribution. If this parameter approaches infinity, the Negative Binomial Distribution approaches a Poisson distribution. In practice, values above 30 lead to convergence. $r$ is estimated in the model itself.

@@

  # Autoregressive process for remaining years
  for(t in 2:(nYears)) {
    # The actual number of sites per year
    nSites[t] ~ dnegbin(prob[t],r)
    prob[t] <- r/(r+lambda[t])

@@

  #r ~ dunif(0,10000)
  #r ~ dgamma(0.5,0.5)
  #r ~ dlnorm(6,1)
  r.cauchy ~ dt(mu = 0, sigma = 5, df = 1)
  r <- abs(r.cauchy)

@@

```{r}
model_monitors <- c("PopDens", "p", "r")
```

@@

# Spare 2 cores from the calculation
ncore <- detectCores() - 2
ncore <- max(ncore, 1)

@@

```{r}
# Initialize with non-convergence
converged <- F
progress <- data.frame(tick = vector(),
                        mean_psrf = vector(),
                        max_psrf = vector())
tick <- 1

@@

  tick <- tick + 1
  # run the model for another batch, with resetting the values (burn-in)
  mcmcSamples <- clusterEvalQ(cl, {
    CmodelMCMC$run(batches, reset = FALSE, resetMV = TRUE)
    return(as.mcmc(as.matrix(CmodelMCMC$mvSamples)))
  })

@@

  progress <- rbind(progress,
                     data.frame(tick = tick,
                        mean_psrf = mean(psrf),
                        max_psrf = max(psrf)))
  # optional: create an mcmc traceplot for visual inspection
  #MCMCtrace(window(mcmcSamples, start = (batches/thinning)-min((batches/thinning),5000)), params = "PopDens", pdf = F)
}

@@

It is already clear here that the basic structure and the (mean) values of the estimation do not differ significantly from the Poisson model. As expected, the credibility intervals are larger because an additional degree of freedom has been introduced by the free variance.

@@

The model still trusts mainly the openness index, the aoristic sum and the dendro data play a subordinate role. The sum calibration has a higher weight.

Der Parameter für die Überdispersion $r$ ist ja auch im Modell geschätzt worden. Folgende Graphik gibt seine Verteilung wieder:

```{r}
MCMCchains(mcmcSamples, params = "r") %>%
  as.data.frame %>%
  pivot_longer(everything()) %>%
  ggplot(aes(x = value, y = name)) + stat_halfeye() + xlim(0,1000)
```

Let's take a look at the effective samples:

@@

  ness <- ness[!(names(ness) %in% c("r", "r.cauchy")) ]

@@

  # just in case: store the result in a RDS file for later inspection  
  saveRDS(collector, file = normalizePath(
  file.path(here(), "data","result_data", "mcmc_collector_neg_binomial.RDS"), mustWork = F
  ))
}

@@

Please note that I excluded 'r' and 'r.cauchy' from the list of parameters that need at least 10000 effective samples. Having that in prolongues the calculation by a factor of 4, which might not be necessary in this context.

@@

```{r}
collector <- readRDS(file = normalizePath(
  file.path(here(), "data","result_data", "mcmc_collector_neg_binomial.RDS")
  ))
```

@@

# MCMCvis methods are rather memory intensive. We implement the summary from scratch
all_chains <- collector[[1]]
for(i in seq_along(collector)) {
  if (i==1) next
  all_chains <- rbind(all_chains, collector[[i]])
}

@@

```{r}
PopDens_summary <- this_mcmc_summary[grep("^PopDens", params),]
PopDens_summary$age <- rev(all_proxies_orig$age)
write.csv(PopDens_summary,
          file = normalizePath(
            file.path(here(), "data","preprocessed_data", "popdens_summary_neg_poisson.csv"
                      ),
            mustWork = F)
          )
```

@@

proxies_and_result <- rbind(melt(all_proxies_orig, id.vars = "age"),
                            melt(PopDens_summary[,1:4], id.vars = "age")
)

@@

It can be seen that the result is essentially very similar to the poisson model, only that the credibility intervalls are slightly bigger.

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popdens_estimation_neg_binomial.pdf"), mustWork = F),
       plot = popdens_plot_adjusted, width = 21, height = 29.7/2, units = "cm")
```

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","p_estimation_neg_binomial.pdf"), mustWork = F),
       plot = p_plot, width = 21, height = 29.7/2, units = "cm")
```
Also interesting is the variation coefficient from the estimation of the Population density:

@@

```{r}
ggsave(normalizePath(file.path(here(), "figures","popvar_plot_neg_binomial.pdf"), mustWork = F),
       plot = popvar_plot, width = 21, height = 29.7/2, units = "cm")
```

And finally, how "Poisson-like" is the Negative Binomial, that means, how large is 'r'? If r tends to infinity, than the Negative Binomial Distribution approaches the Poisson Distribution. Values over 50 are considered to be essential binomial.

r_plot <- 
  all_chains[,"r"] %>%
  as.data.frame %>%
  pivot_longer(everything()) %>%
  ggplot(aes(x = value, y = name)) + stat_halfeye() +
  xlim(0,1000) + xlab("Value of R") + ylab("") + theme_minimal()
r_plot
```

Or, to give the values of r more numerical:

```{r}
this_mcmc_summary["r",]
```

There is quite a range, since there is no real difference once the value surpasses the threshold to become "Poisson-like". But it indicates quite clearly, that even when we model with variable variance, the model tends strongly to converge on a poisson-like solution. We can take this as indication that a more restrictive Poisson model is not an unreasonable choice.

### 2022-12-08 analysis/sensitivity_analysis.Rmd

---
title: "Sensitivity Analysis"
author: "Martin Hinz"
date: "2022-11-20"
output:
  pdf_document: default
  html_document:
    keep_md: yes
bibliography: references.bib
---

>>>>

---
title: "Sensitivity Analysis"
author: "Martin Hinz"
date: "2022-11-20"
output:
  html_document:
    keep_md: yes
  pdf_document: default
bibliography: references.bib
---
